The Quantum Sneakernet

### 2020-08-29 Sections/quantum_channels.tex
editing Saturday night

\subsection{Quantum processes} \index{Quantum processes}

@@

The first stage in QPT is \textit{quantum state tomography} (QST), where the goal is to reconstruct and unknown density matrix via measurements upon multiple copies of the state. QST is based upon the simple observation that the completeness relation\index{Completeness relation} for an arbitrary state can be expressed,
\begin{align}
\hat\rho = \sum_i \mathrm{tr}(\hat{E}_i\hat\rho)\cdot\hat{E}_i,
\end{align}
where $\{\hat{E}_i\}$ forms a complete basis for the Hilbert space of $\hat\rho$. For a single qubit this decomposition is most often performed in the Pauli basis, 
\begin{align}
\hat\rho = \mathrm{tr}(\hat\rho)\cdot\hat\openone + \mathrm{tr}(\hat{X}\hat\rho)\cdot\hat{X} + \mathrm{tr}(\hat{Y}\hat\rho)\cdot\hat{Y} +\mathrm{tr}(\hat{Z}\hat\rho)\cdot\hat{Z}.
\end{align}
Of course, \mbox{$\mathrm{tr}(\hat{E}\hat\rho) = P(\hat{E}|\hat\rho)$} is just the expectation value of the measurement operator $\hat{E}$ when measuring $\hat\rho$. Thus, measuring the expectation values in each of the four Pauli bases reconstructs $\hat\rho$.

>>>>

\subsection{Quantum processes}\label{sec:quantum_processes}\index{Quantum processes}

@@

The first stage in QPT is \textit{quantum state tomography} (QST), where the goal is to reconstruct and unknown density matrix via measurements upon multiple copies of the state. QST is based upon the simple observation that the completeness relation\index{Completeness relation} for an arbitrary state can be expressed,
\begin{align}
\hat\rho = \sum_i \mathrm{tr}(\hat{E}_i\hat\rho)\cdot\hat{E}_i,
\end{align}
where $\{\hat{E}_i\}$ forms a complete basis for the Hilbert space of $\hat\rho$. For a single qubit this decomposition is most often performed in the Pauli basis, 
\begin{align}
\hat\rho &= \mathrm{tr}(\hat\rho)\cdot\hat\openone + \mathrm{tr}(\hat{X}\hat\rho)\cdot\hat{X} + \mathrm{tr}(\hat{Y}\hat\rho)\cdot\hat{Y} +\mathrm{tr}(\hat{Z}\hat\rho)\cdot\hat{Z} \nonumber\\
	&= \sum_{i=1}^4 \mathrm{tr}(\hat{\sigma}_i\hat\rho)\cdot\hat{\sigma}_i,
\end{align}
where $\sigma_i$ denote the four Pauli operators. Of course, \mbox{$\mathrm{tr}(\hat{E}\hat\rho) = P(\hat{E}|\hat\rho)$} is just the expectation value of the measurement operator $\hat{E}$ when measuring $\hat\rho$. Thus, measuring the expectation values in each of the four Pauli bases reconstructs $\hat\rho$.

### 2020-08-29 Simon's section/main.tex
different blind and verification file
editing Saturday night

All of these techniques employ photons as the carrier of quantum information and have already been deployed in QKD protocols \cite{SD-Schmitt-Manderbach:2007aa,SD-Peev:2009aa,SD-Liao:2017aa}. However, there are several issues with these techniques that could make building a global quantum network challenging.

While QKD remains the foremost protocol deployed on current quantum communication hardware, a true global quantum internet must handle a vast array of potential applications, including linking fully error-corrected quantum computing systems \cite{SD-Devitt2011,SD-Fitzsimons:2017aa}. Consequently, we need to consider several metrics in potential hardware implementations. Four primary metrics can be identified:
\begin{itemize}
\item Speed: How many qubits can be transmitted per second?
\item Distance: How far can we transmit qubits, while maintaining the required speed?
\item Fidelity: How accurately can each qubit be transmitted, while maintaining the required speed and distance?
\item Cost: What is the monetary cost of building, deploying and maintaining the hardware underlying a quantum channel of given speed, distance, and fidelity?
\end{itemize}

@@

In this chapter we discuss some of the practical demands that must be taken into account when constructing a quantum internet (in the context of QKD), and introduce a fourth type of model for global quantum networking, the quantum Sneakernet \cite{SD-Devitt:2016aa}. We will take a qualitative look at its structure and operation, and argue that there are many potential practical and economic merits to employing it as the backbone technology in a global network.

@@

Considering the major, well-developed qubit technologies, we summarise their relative advantages and disadvantages. In many systems, \textit{infrastructure requirements} appear to be the most significant barrier to portability. These major technologies are:
\begin{itemize}
\item \textbf{Superconducting qubits}\index{Superconducting qubits}: require operational temperatures of $\sim$30mK to maintain operational coherence. Such temperatures require dilution refrigeration\index{Dilulion refrigeration}, which is clumsy and undermines portability. 
\item \textbf{Ion traps}\index{Ion traps}: require an almost perfect vacuum environment, which again may prove to be implementationally problematic. 
\item \textbf{Linear optics}\index{Linear optics}: avoids issues such as vacuums and extremely low temperatures, but gate non-determinism introduces -- currently -- impractical physical overheads. 
\item \textbf{Quantum dots}\index{Quantum dots}: similar to superconducting technology, dilution refrigeration is required.
\item \textbf{Phosphorus in Silicon}\index{Phosphorus in Silicon}: Also requires dilution refrigeration. 
\item \textbf{Colour centres (e.g. NV-diamond)}\index{Colour centres}\index{NV-diamond}: Neither vacuums nor dilution refrigeration are required. 
\end{itemize}

@@

Active QEC protocols are central to a Sneakerent communications architecture. A Quantum Memory Unit (QMU)\index{Quantum memory units} is ideally designed to house an array of optically coupled qubits that are encoded using QEC into a long-lived quantum memory. Without loss of generality, we will use a particular, well-known error correction technique to illustrate the basic operational principles of a QMU, and how they can be scaled up to the scale necessary for a quantum Sneakernet network.

@@

The surface code has been extremely well studied over the past 15 years. We have extremely accurate simulations that detail the threshold behaviour of the code under a variety of different assumptions and we have quantified very well how the scaling of the code behaves as a function of physical error rate \cite{SD-Stace:2010aa,SD-Wang:2011aa,SD-Stephens:2014aa,SD-Nagayama:2017aa,SD-Tuckett:2018aa}. For this reason we are able to quantify expected \textit{logical} memory time, $T$, in terms of the physical operation time of the quantum gates in our hardware, $t$, the number of physical qubits in the QMU array, $N$, and the logical error rate we want to target, $P$. Through direct numerical simulation, we find \cite{SD-Devitt:2016aa},
\begin{align} \label{eq:scale}
T \approx 10t\sqrt{N} P(70p)^{-\sqrt{N}/4},
\end{align}
where $p$ is the physical error rate associated with each of the qubits within each QMU -- assumed to be at least below the fault-tolerant threshold of the planar code, $p_\mathrm{th} \approx 0.7\%$ \cite{SD-Fowler:2012aa}.

@@

It should be emphasised that the estimates in Fig.~\ref{fig:array} are based on QEC techniques that are unoptimised for a specific hardware chipset. Performing error correction decoding on a system with biased noise \cite{SD-Tuckett:2018aa} can change resource overheads and it is possible for other QEC coding techniques to be invented that is compatible with hardware engineering constraints that scales better than Eq.~(\ref{eq:scale}) for the rotated planar code \cite{SD-Bombin:2015aa,SD-Breuckmann:2017aa,SD-Fawzi:2018aa}. This could reduce the required physical qubit array sizes for a given QMU memory. However, the key message here is that a physical qubit array of on the order of 1cm$^2$, with physical gate times of order 1$\mu$s can be made into very long-lived quantum memories using the same architectural structures and assumptions of quantum computing systems that are already under development (we just require the added property of portability) \cite{SD-Jones:2012aa,SD-Gimeno-Segovia:2015aa,SD-Nemoto:2014aa,SD-Hill:2015aa,SD-Lekitsch:2017aa}.

@@

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{cost}
	\caption{Exponential decrease of the cost of classical transistors over the past 50 years.  Plot was constructed using data from \cite{SD-Berndt2000,} } \label{fig:price}.
\end{figure}

While it is certainly not expected that the price-per-qubit (PPQ) will reach these levels anytime soon, we need to keep Fig.~\ref{fig:price} in mind if we ultimately want to make quantum technology at the scale needed to take full advantage of the power of quantum computing and communications.

This issue of PPQ is of critical concern for large-scale quantum computing systems. Shown in Fig.~\ref{fig:price} are costing out of a quantum computing system of sufficient size to perform Shor's factoring algorithm for large key sizes and for quantum simulation of nitrogenase\index{Nitrogenase} molecules for nitrogen fixation \cite{SD-Fowler:2012aa,SD-Reiher:2017aa}. If an ultimate PPQ goal is not \$1 or lower, there may be little economic motivation for building more than a handful of quantum computers globally. It should be noted that PPQ needs to take into account the infrastructure and control systems as well as the physical qubit itself. For example, in superconducting systems, the required dilution refrigeration system is expensive -- around \$500,000. Additionally, the sample chamber for the dilution refrigerator is quite small in comparison to the `footprint' of a superconducting qubit. A commercial dilution refrigeration system can accommodate perhaps 100 such physical qubits. Consequently, at a minimum, the PPQ in this system would be \$5,000. Additionally Fig.~\ref{fig:price} does not include any R\&D expenditure or the costs associated with building the fabrication infrastructure to build the qubits themselves.

@@

The basic operational primitive of the quantum Sneakernet system is an old technique for the long range distribution of information. As encapsulated in this wonderful quote from the former director of the University of Toronto Computing Services (UTCS):
\\
\\
\famousquote{Never underestimate the bandwidth of a station wagon full of tapes hurtling down the highway.}{Warren Jackson}
\\
\\
While essentially everyone today is familiar with the principle of classical Sneakernets, many people are not familiar with the name \href{https://en.wikipedia.org/wiki/Sneakernet}{https://en.wikipedia.org/wiki/Sneakernet}. Rather than sending information via radio waves or fibre optic cables, information it's loaded onto storage memory and physically transported from source to destination. The viability of Sneakernets in the classical world depends heavily on three practical considerations:
\begin{itemize}
\item Availability of cheap, high capacity classical memories
\item Limited bandwidth and high costs associated with radio or optical fibre communications channels
\item The need or lack of need for low latency communications 
\end{itemize}

@@

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{SWAPPING}
	\caption{A backbone network of physically shipping a large volume of QuSTICKS between a home office and regional office can generate continuous Bell states between these two locations.  Alice and Bob can take QuSTICK units from the two respective offices and travel to a third location where they meet.  If an authentication protocol is needed -- because Alice and Bob have never met and need to know they have come from the same organisation -- the entanglement in each of their QuSTICKS can be SWAPPED by their respective offices such that they now share Bell states together.  These Bell states can then be used to violate a Bell inequality, authenticating that their quantum resource was given to them by the same source.} \label{fig:SWAPPING}
\end{figure}

@@

The processes described above enable a persistent network to exist. Even though users will consume QuSTICK entanglement whenever they use their device to perform a quantum communications protocol, that networked entanglement can be replenished easily. Again, the nature and structure of a sneakernet network allows us considerable flexibility in network topology. We can essentially design a two-stage embedded network: One stage in which the structure of the network is determined by the physical interaction of the users who have access to physical QuSTICKs, and a second stage in which quantum information flow is dictated by the structure of the underlying entanglement network. This is inconceivable in the classical world of information networking. We can only begin to imagine what remarkable things are possible with this kind of technology infrastructure. We can be certain that it will unlock capabilities well beyond the basic ultra-high security quantum communications applications that we are discussing here.

@@

The key question that the authentication process must answer is this: How do we ensure that messages are coming from the requisite trusted source? A quantum sneakernet solution is similar to physical authentication tokens that some bank customers are given to access their accounts for high-value transactions. These classical authentication tokens utilise a variety of methods to ensure that the server (e.g. a bank website) and the client (the person with a bank account) can share a secret message that can be used to authenticate a log-in session. Some utilise static password tokens, some use synchronous dynamic tokens and some use a type of `call and response' method. There are even services that use a smart phone APP to verify the phone's SIM card and then generate a one-time key. All of these techniques are vulnerable to security flaws that present themselves if:
\begin{enumerate}
\item The implementation is imperfect.
\item The token is lost, stolen, or duplicated.
\item If some classical calculation that was assumed to be computationally difficult is compromised in some way. 
\end{enumerate}

@@

{\em QKD protocols address only the problem of agreeing on keys for encrypting data. Ubiquitous on-demand modern services, such as verifying identities and data integrity, establishing network sessions, providing access control, and automatic software updates, rely on authentication and integrity mechanisms (e.g. digital signatures) as well as encryption.}

@@

{\em The two major functional limitations of commercial QKD systems are the relatively short effective range of transmission, and the fact that BB84 and similar proposals are fundamentally point-to-point protocols. This means that QKD does not integrate easily with the Internet or with the mobile technologies, apps and services that dominate public and business life today.}

@@

While we have illustrated much of the function of the Sneakernet system through point-to-point protocols\index{Point-to-point!Protocols} between two parties, the design is a fully-formed quantum network. Entanglement can be distributed and shared between an arbitrary number of parties and more complex protocols, such as secret sharing or distributed communication/computation, can be performed. In the context of QKD, we do not utilise the point-to-point protocol of BB84. Instead we base QKD protocols on the more advanced E91\index{E91 protocol} (which utilises two properties of entanglement, the perfect correlation of measurements made by Alice and Bob as well as the ability to detect eavesdropping by noting disturbances in the quality of that correlation). A Sneakernets ability to distribute, share and maintain entanglement on global distances makes Ekert-91 practical for real-world cryptography for the first time.

@@

{\em Any real-world QKD system will be built from classical components, such as sources, detectors and fibres, and potentially ancillary classical network devices, any one of which may prove to be a weak link. A number of attacks have been proposed and demonstrated on deployed QKD systems that subvert one of more of these hardware components, enabling the secret shared key to be recovered without triggering an alarm.}

Sources, detectors and fibres are not components of the Sneakernet system. The integrity of the network rests with the functional integrity of individual QuSTICKs. As these units will be continuously moved, entangled locally, and then moved again, QuSTICKs can be tested and verified when the entanglement is initially prepared. Various unit testing can be performed between two QuSTICKs at home base to ensure quantum integrity of the system before they are ever deployed in the field. Compromised units can be removed from the network or returned for a complete rebuild and redeployment. Any units that become compromised in the field will be detected through the entanglement links that were initially prepared when QuSTICKs were present at home base. As no further entanglement operations are performed between QuSTICK units \textit{after} they have been locally entangled and verified, points of failure (where security could be affected) are drastically reduced.

{\em Denial of service (DoS)\index{Denial of service (DoS) attacks} attacks that interfere with the paths carrying the QKD transmissions also seem potentially easier with QKD than with contemporary Internet or mobile network technologies. Since QKD devices typically abort a key establishment session when they detect tampering, this makes it difficult to recommend QKD for contexts where DoS attacks are likely to be attempted.}

@@

\subsection{The ups and downs of the quantum Sneakernet}

\comment{To do}

\comment{No interception, bandwidth, dos requires destroying endpoints since no channels}

\subsection{A vision for the future: Creating a sneakernet based quantum internet}

@@

\section{Moore's Law in the quantum era}\index{Quantum Moore's Law}

\comment{To do}

>>>>

All of these techniques employ photons as the carrier of quantum information and have already been deployed in QKD protocols \cite{SD-Schmitt-Manderbach:2007aa, SD-Peev:2009aa, SD-Liao:2017aa}. However, there are several issues with these techniques that could make building a global quantum network challenging.

While QKD remains the foremost protocol deployed on current quantum communication hardware, a true global quantum internet must handle a vast array of potential applications, including linking fully error-corrected quantum computing systems \cite{SD-Devitt2011,SD-Fitzsimons:2017aa}. Consequently, we need to consider several metrics in potential hardware implementations. Four primary metrics can be identified:
\begin{itemize}
\item Speed: How many qubits can be transmitted per second?
\item Distance: How far can we transmit qubits, while maintaining the required speed?
\item Fidelity: How accurately can each qubit be transmitted, while maintaining the required speed and distance?
\item Cost: What is the monetary cost of building, deploying and maintaining the hardware underlying a quantum channel with given speed, distance, and fidelity?
\end{itemize}

@@

In this chapter we discuss some of the practical demands that must be taken into account when constructing a quantum internet (in the context of QKD), and introduce a fourth type of model for global quantum networking, the quantum Sneakernet \cite{SD-Devitt:2016aa}. We will take a qualitative look at its structure and operation, and argue that there are many potential practical and economic merits of employing it as the backbone technology in a global network.

@@

Considering the major, well-developed qubit technologies, we summarise their relative advantages and disadvantages. In many systems, \textit{infrastructure requirements} appear to be the most significant barrier to portability. These major technologies are:
\begin{itemize}
\item \textbf{Superconducting qubits}\index{Superconducting qubits}: require operational temperatures of $\sim$30mK to maintain operational coherence. Such temperatures require dilution refrigeration\index{Dilution refrigeration}, which is clumsy and undermines portability. 
\item \textbf{Ion traps}\index{Ion traps}: require an almost perfect vacuum environment, which again may prove to be implementationally problematic. 
\item \textbf{Linear optics}\index{Linear optics}: avoids issues such as vacuums and extremely low temperatures, but gate non-determinism introduces -- currently -- impractical physical overheads. 
\item \textbf{Quantum dots}\index{Quantum dots}: similar to superconducting technology, dilution refrigeration is required.
\item \textbf{Phosphorus in Silicon}\index{Phosphorus in Silicon}: Also requires dilution refrigeration. 
\item \textbf{Colour centres (e.g. NV-diamond)}\index{Colour centres}\index{NV-diamond}: Neither vacuums nor dilution refrigeration are required. 
\end{itemize}

@@

Active QEC protocols are central to a Sneakernet communications architecture. A Quantum Memory Unit (QMU)\index{Quantum memory units} is ideally designed to house an array of optically coupled qubits that are encoded using QEC into a long-lived quantum memory. Without loss of generality, we will use a particular, well-known error correction technique to illustrate the basic operational principles of a QMU, and how they can be scaled up to the scale necessary for a quantum Sneakernet network.

@@

The surface code has been extremely well studied over the past 15 years. We have extremely accurate simulations that detail the threshold behaviour of the code under a variety of different assumptions and we have quantified very well how the scaling of the code behaves as a function of physical error rate \cite{SD-Stace:2010aa, SD-Wang:2011aa, SD-Stephens:2014aa, SD-Nagayama:2017aa, SD-Tuckett:2018aa}. For this reason we are able to quantify expected \textit{logical} memory time, $T$, in terms of the physical operation time of the quantum gates in our hardware, $t$, the number of physical qubits in the QMU array, $N$, and the logical error rate we want to target, $P$. Through direct numerical simulation, we find \cite{SD-Devitt:2016aa},
\begin{align} \label{eq:scale}
T \approx 10t\sqrt{N} P(70p)^{-\sqrt{N}/4},
\end{align}
where $p$ is the physical error rate associated with each of the qubits within each QMU -- assumed to be at least below the fault-tolerant threshold of the planar code, $p_\mathrm{th} \approx 0.7\%$ \cite{SD-Fowler:2012aa}.

@@

It should be emphasised that the estimates in Fig.~\ref{fig:array} are based on QEC techniques that are unoptimised for a specific hardware chipset. Performing error correction decoding on a system with biased noise \cite{SD-Tuckett:2018aa} can change resource overheads and it is possible for other QEC coding techniques to be invented that is compatible with hardware engineering constraints that scales better than Eq.~(\ref{eq:scale}) for the rotated planar code \cite{SD-Bombin:2015aa,SD-Breuckmann:2017aa,SD-Fawzi:2018aa}. This could reduce the required physical qubit array sizes for a given QMU memory. However, the key message here is that a physical qubit array of on the order of 1cm$^2$, with physical gate times of order 1$\mu$s can be made into very long-lived quantum memories using the same architectural structures and assumptions of quantum computing systems that are already under development (we just require the added property of portability) \cite{SD-Jones:2012aa, SD-Gimeno-Segovia:2015aa, SD-Nemoto:2014aa, SD-Hill:2015aa, SD-Lekitsch:2017aa}.

@@

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{cost}
	\caption{Exponential decrease of the cost of classical transistors over the past 50 years.  Plot was constructed using data from \cite{SD-Berndt2000}.} \label{fig:price}.
\end{figure}

While it is certainly not expected that the price per qubit (PPQ) will reach these levels anytime soon, we need to keep Fig.~\ref{fig:price} in mind if we ultimately want to make quantum technology at the scale needed to take full advantage of the power of quantum computing and communications.

This issue of PPQ is of critical concern for large-scale quantum computing systems. Shown in Fig.~\ref{fig:price} are costing out of a quantum computing system of sufficient size to perform Shor's factoring algorithm for large key sizes and for quantum simulation of nitrogenase\index{Nitrogenase} molecules for nitrogen fixation \cite{SD-Fowler:2012aa, SD-Reiher:2017aa}. If an ultimate PPQ goal is not \$1 or lower, there may be little economic motivation for building more than a handful of quantum computers globally. It should be noted that PPQ needs to take into account the infrastructure and control systems as well as the physical qubit itself. For example, in superconducting systems, the required dilution refrigeration system is expensive -- around \$500,000. Additionally, the sample chamber for the dilution refrigerator is quite small in comparison to the `footprint' of a superconducting qubit. A commercial dilution refrigeration system can accommodate perhaps 100 such physical qubits. Consequently, at a minimum, the PPQ in this system would be \$5,000. Additionally Fig.~\ref{fig:price} does not include any R\&D expenditure or the costs associated with building the fabrication infrastructure to build the qubits themselves.

@@

The basic operational primitive of the quantum Sneakernet system is an old technique for the long range distribution of information. As encapsulated in this wonderful quote from the former director of the University of Toronto Computing Services (UTCS):
\\
\\
\famousquote{Never underestimate the bandwidth of a station wagon full of tapes hurtling down the highway.}{Warren Jackson}
\\
\\
While essentially everyone today is familiar with the principle of classical Sneakernets, many people are not familiar with the name \href{https://en.wikipedia.org/wiki/Sneakernet}{https://en.wikipedia.org/wiki/Sneakernet}. Rather than sending information via radio waves or fibre optic cables, information it's loaded onto storage memory and physically transported from source to destination. The viability of Sneakernets in the classical world depends heavily on three practical considerations:
\begin{itemize}
\item Availability of cheap, high capacity classical memories.
\item Limited bandwidth and high costs associated with radio or optical fibre communications channels.
\item The need or lack of need for low latency communications.
\end{itemize}

@@

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{swapping}
	\caption{A backbone network of physically shipping a large volume of QuSTICKS between a home office and regional office can generate continuous Bell states between these two locations.  Alice and Bob can take QuSTICK units from the two respective offices and travel to a third location where they meet.  If an authentication protocol is needed -- because Alice and Bob have never met and need to know they have come from the same organisation -- the entanglement in each of their QuSTICKS can be SWAPPED by their respective offices such that they now share Bell states together.  These Bell states can then be used to violate a Bell inequality, authenticating that their quantum resource was given to them by the same source.} \label{fig:SWAPPING}
\end{figure}

@@

The processes described above enable a persistent network to exist. Even though users will consume QuSTICK entanglement whenever they use their device to perform a quantum communications protocol, that networked entanglement can be replenished easily. Again, the nature and structure of a Sneakernet network allows us considerable flexibility in network topology. We can essentially design a two-stage embedded network: One stage in which the structure of the network is determined by the physical interaction of the users who have access to physical QuSTICKs, and a second stage in which quantum information flow is dictated by the structure of the underlying entanglement network. This is inconceivable in the classical world of information networking. We can only begin to imagine what remarkable things are possible with this kind of technology infrastructure. We can be certain that it will unlock capabilities well beyond the basic ultra-high security quantum communications applications that we are discussing here.

@@

The key question that the authentication process must answer is this: How do we ensure that messages are coming from the requisite trusted source? A quantum Sneakernet solution is similar to physical authentication tokens that some bank customers are given to access their accounts for high-value transactions. These classical authentication tokens utilise a variety of methods to ensure that the server (e.g. a bank website) and the client (the person with a bank account) can share a secret message that can be used to authenticate a log-in session. Some utilise static password tokens, some use synchronous dynamic tokens and some use a type of `call and response' method. There are even services that use a smart phone APP to verify the phone's SIM card and then generate a one-time key. All of these techniques are vulnerable to security flaws that present themselves if:
\begin{enumerate}
\item The implementation is imperfect.
\item The token is lost, stolen, or duplicated.
\item If some classical calculation that was assumed to be computationally difficult is compromised in some way. 
\end{enumerate}

@@

\textit{QKD protocols address only the problem of agreeing on keys for encrypting data. Ubiquitous on-demand modern services, such as verifying identities and data integrity, establishing network sessions, providing access control, and automatic software updates, rely on authentication and integrity mechanisms (e.g. digital signatures) as well as encryption.}

@@

\textit{The two major functional limitations of commercial QKD systems are the relatively short effective range of transmission, and the fact that BB84 and similar proposals are fundamentally point-to-point protocols. This means that QKD does not integrate easily with the Internet or with the mobile technologies, apps and services that dominate public and business life today.}

@@

While we have illustrated much of the function of the Sneakernet system through point-to-point protocols\index{Point-to-point!Protocols} between two parties, the design is a fully-formed quantum network. Entanglement can be distributed and shared between an arbitrary number of parties and more complex protocols, such as secret sharing or distributed communication/computation, can be performed. In the context of QKD, we do not utilise the point-to-point protocol of BB84. Instead we base QKD protocols on the more advanced E91\index{E91 protocol} (which utilises two properties of entanglement, the perfect correlation of measurements made by Alice and Bob as well as the ability to detect eavesdropping by noting disturbances in the quality of that correlation). A Sneakernet's ability to distribute, share and maintain entanglement on global distances makes Ekert-91 practical for real-world cryptography for the first time.

@@

\textit{Any real-world QKD system will be built from classical components, such as sources, detectors and fibres, and potentially ancillary classical network devices, any one of which may prove to be a weak link. A number of attacks have been proposed and demonstrated on deployed QKD systems that subvert one of more of these hardware components, enabling the secret shared key to be recovered without triggering an alarm.}

Sources, detectors and fibres are not components of the Sneakernet system. The integrity of the network rests with the functional integrity of individual QuSTICKs. As these units will be continuously moved, entangled locally, and then moved again, QuSTICKs can be tested and verified when the entanglement is initially prepared. Various unit testing can be performed between two QuSTICKs at home base to ensure quantum integrity of the system before they are ever deployed in the field. Compromised units can be removed from the network or returned for a complete rebuild and redeployment. Any units that become compromised in the field will be detected through the entanglement links that were initially prepared when QuSTICKs were present at home base. As no further entanglement operations are performed between QuSTICK units \textit{after} they have been locally entangled and verified points of failure (where security could be affected) are drastically reduced.

\textit{Denial of service (DoS)\index{Denial of service (DoS) attacks} attacks that interfere with the paths carrying the QKD transmissions also seem potentially easier with QKD than with contemporary Internet or mobile network technologies. Since QKD devices typically abort a key establishment session when they detect tampering, this makes it difficult to recommend QKD for contexts where DoS attacks are likely to be attempted.}

@@

\subsection{A vision for a Sneakernet based quantum internet}

@@
